Solar wind prediction for the Parker Solar Probe orbit

### 2017-06-09 paperMVVB/sections/content.tex
derived median perihelia speed for figs 11 and 12

\subsection{PSP solar wind environment estimation}
Implementing the orbital distance data and predicted SSN for the mission time we can derive PSP's estimated solar wind environment $W'''(x,ssn,r)$.\\
The zoom into the first and the nearest perihelia show which solar wind parameter magnitudes can be expected there (Figs.~\ref{fig:SPP_perihelia_prediction_d_plot} and \ref{fig:SPP_perihelia_prediction_nearest_d_plot}).\\
\begin{figure}
	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_d_plot.pdf}}
	\caption{Estimated solar wind parameter medians (black) and their error bands (grey) during PSP's first perihelion in 2018 at about \SI{0.16}{\au}. For the velocity the SSN independent slow and fast parts are plotted.}
	\label{fig:SPP_perihelia_prediction_d_plot}
\end{figure}
\begin{figure}
	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_nearest_d_plot.pdf}}
	\caption{Estimated solar wind parameter medians (black) and their error bands (grey) during PSP's nearest perihelion in 2024 at \SI{0.0459}{\au}. For the velocity the SSN independent slow and fast parts are plotted.}
	\label{fig:SPP_perihelia_prediction_nearest_d_plot}
\end{figure}

>>>>

\subsection{PSP solar wind environment estimation}
Implementing the orbital distance data and predicted SSN for the mission time we can derive PSP's estimated solar wind environment $W'''(x,ssn,r)$.\\
The zoom into the first and the nearest perihelia show which solar wind parameter magnitudes can be expected there (Figs.~\ref{fig:SPP_perihelia_prediction_e_plot} and \ref{fig:SPP_perihelia_prediction_nearest_e_plot}).\\
\begin{figure}
	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_e_plot.pdf}}
	\caption{Estimated solar wind parameter medians (black) and their error bands (grey) during 12 days in 2018 with PSP's first perihelion at about \SI{0.16}{\au}. For the velocity the combined median is calculated and also the SSN independent slow and fast parts are plotted (dotted).}
	\label{fig:SPP_perihelia_prediction_e_plot}
\end{figure}
\begin{figure}
	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_nearest_e_plot.pdf}}
	\caption{Estimated solar wind parameter medians (black) and their error bands (grey) during during 12 days in 2024 with PSP's nearest perihelion at \SI{0.0459}{\au}. For the velocity the combined median is calculated and also the SSN independent slow and fast parts are plotted (dotted).}
	\label{fig:SPP_perihelia_prediction_nearest_e_plot}
\end{figure}
